\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-08-06 paper/paper.tex
Updates.

\begin{figure}
  \centering
  \scriptsize
\begin{verbatim}
    // Apply ganged operation
    event_apply_ganged_op (packet, barrier)
    {
      if(co-ordinator)
        atomic set bit me in barrier.mask         
        do
         for each participant p in operation
          if public_data[p].view > packet.view
           barrier.failed = true 
           atomic set bit for p in barrier.mask
        while barrier.mask != mask of all participants
        if barrier.failed
         send retry to client
        else       
         execute operation
         send response
      else
        wait until 
         public_data[co-ordinator].view > packet.view OR
         barrier.mask == mask of participating cores
        if public_data[co-ordinator].view > packet.view OR
           barrier.failed
         send retry to client
        else
         execute operation
    }
\end{verbatim}
\caption{Ganged Operation}
\label{fig:ganged_ops}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/flashlog_512.pdf}
\caption{Second level log with 512 bytes payload}
\label{fig:flashlog_512}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/multi.pdf}
\caption{Ganged Operations}
\label{fig:ganged}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/kv_baseline.pdf}
\caption{Baseline KV replication performance}
\label{fig:kv_baseline}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/rocksdb.pdf}
\caption{Rocksdb - small updates}
\label{fig:rocksdb}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{results2/rocksdb_256.pdf}
\caption{Rocksdb - large updates}
\label{fig:rocksdb_256}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/rocksdb_multi.pdf}
\caption{Rocksdb - batched writes}
\label{fig:rocksdb_multi}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/fb.pdf}
\caption{Rocksdb - read heavy workload}
\label{fig:fb}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.6]{results2/fb2.pdf}
\caption{Rocksdb - write heavy workload}
\label{fig:fb2}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{results2/failover.pdf}
\caption{Rocksdb - failover}
\label{fig:timeline}
\end{figure}

@@

The scalable commutativity rule~\cite{scalable_commutativity} generalizes the
idea of commutativity in key value store interfaces that we have used for
horizontal scaling in Cyclone. Conveniently, it provides a tool for checking when
API calls can commute in a history. It is a simple exercise to express a key
value store API in COMMUTER and check that operations to different keys
commute. This provides a theoretical basis for horizontal scaling, something we
have omitted for brevity from this paper. The scalable commutativity rule also
suggests that scalable key value store implementations such as
FloDB~\cite{flodb} would necessarily have commutative interfaces, enabling more
general applicability of Cyclone.

>>>>

\begin{figure}
  \centering
  \scriptsize
  \bf
\begin{verbatim}
    // Apply ganged operation
    event_apply_ganged_op (packet, barrier)
    {
      if(co-ordinator)
        atomic set bit me in barrier.mask         
        do
         for each participant p in operation
          if public_data[p].view > packet.view
           barrier.failed = true 
           atomic set bit for p in barrier.mask
        while barrier.mask != mask of all participants
        if barrier.failed
         send retry to client
        else       
         execute operation
         send response
      else
        wait until 
         public_data[co-ordinator].view > packet.view OR
         barrier.mask == mask of participating cores
        if public_data[co-ordinator].view > packet.view OR
           barrier.failed
         send retry to client
        else
         execute operation
    }
\end{verbatim}
\caption{Ganged Operation}
\label{fig:ganged_ops}
\end{figure}

@@

@@

\begin{figure*}
\begin{minipage}{0.33\textwidth}
  \includegraphics[scale=0.45]{results2/flashlog_512.pdf}
  \caption{Second level log with 512 bytes payload}
  \label{fig:flashlog_512}
\end{minipage}
\begin{minipage}{0.33\textwidth}
  \includegraphics[scale=0.45]{results2/multi.pdf}
  \caption{Ganged Operations}
  \label{fig:ganged}
\end{minipage}
\begin{minipage}{0.33\textwidth}
  \includegraphics[scale=0.45]{results2/kv_baseline.pdf}
  \caption{Baseline KV replication performance}
  \label{fig:kv_baseline}
\end{minipage}
\end{figure*}

@@

@@

\begin{figure*}
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[scale=0.45]{results2/rocksdb.pdf}
    \caption{Rocksdb - small updates}
    \label{fig:rocksdb}
  \end{minipage} 
  \begin{minipage}{0.33\textwidth}
    \includegraphics[scale=0.45]{results2/rocksdb_256.pdf}
    \caption{Rocksdb - large updates}
    \label{fig:rocksdb_256}
  \end{minipage} 
  \begin{minipage}{0.33\textwidth}
    \includegraphics[scale=0.45]{results2/rocksdb_multi.pdf}
    \caption{Rocksdb - batched writes}
    \label{fig:rocksdb_multi}
  \end{minipage}
\end{figure*}

@@

@@

\begin{figure*}
\begin{minipage}{0.33\textwidth}
\includegraphics[scale=0.45]{results2/fb.pdf}
\caption{Rocksdb - read heavy workload}
\label{fig:fb}
\end{minipage}
\begin{minipage}{0.33\textwidth}
  \includegraphics[scale=0.45]{results2/fb2.pdf}
  \caption{Rocksdb - write heavy workload}
  \label{fig:fb2}
\end{minipage}
\begin{minipage}{0.33\textwidth}
  \includegraphics[scale=0.45]{results2/failover.pdf}
  \caption{Rocksdb - failover}
  \label{fig:timeline}
\end{minipage}
\end{figure*}

@@

@@

The scalable commutativity rule~\cite{scalable_commutativity} states that for a
shared memory program to scale in performance with concurrency it must also have
an interface that is commutative for common case invocations. We have also used
interface level commutativity to extract parallelism for the purpose of scaling
replication performance. Others have used the same commutativity to create
per-cpu data structures to scale KV store performance~\cite{flodb}.
